Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
final final

\paragraph{Review $\#$56: “You say that you assume the chair to be human, yet you think he will answer hundreds of questions..?”}
%We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values). 
We do not assume this. We plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually small. Our experiments also show that efficiency decreases only slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
%When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner. We also mention that the process could be terminated early: after a fixed number of questions (the “approximate winner” is the alternative with lowest regret); or after reaching a "low enough" regret.
%In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g. zero in skate and "courses", 8.4 in m5n10, 13 in m5n20, 30 in tshirt,...), this is because the strategy does a good job of asking the question that gives more information, and often only “sparse” information about the voting rule is enough. Similarly, the average number of questions asked to a voter is also reasonable (e.g questions per agent 6.5 in courses, 6.1 in m5n10,  )
%: X.X in Experiment YY, for instance. In Table 2, the (10,20) example shows that to reach a “low” regret -that we define as n/10- we need to ask 340 questions. This number should be divided among the voters and the chair, resulting in ~ 10 questions per voter, which we consider a reasonable amount. The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
%Finally, note that the process could be terminated early: e.g. one could decide to stop after a fixed number of questions (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest minimax regret value.
%If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
\end{document}

>>>>

\paragraph{Review $\#$56: “You say that you assume the chair (…) will answer hundreds of questions..?”}
%We assume the chair to be human and, as discussed in the paragraph “Building concrete questions for the chair“ on page 3, we view questions “what is the winner of this profile” to be easier to answer than directly asking the weights (in the same way as, for the problem of elicitation an utility function, one would ask comparison queries rather than asking directly utility values). 
We do not assume this. We plot the total number of questions in order to have a simple way to compare the total elicitation cost. 
Table 1 of Appendix shows that the number of questions posed to the chair (and each agent) is usually small. Our experiments also show that efficiency decreases only slowly when diminishing the number of questions to the chair and distributing them to the voters instead.
%When the profile is quite homogeneous (see the lines corresponding to real datasets) this number is very low or even zero in case of clear winner. We also mention that the process could be terminated early: after a fixed number of questions (the “approximate winner” is the alternative with lowest regret); or after reaching a "low enough" regret.
%In fact the number of questions asked to the chair using the Pessimistic strategy (as shown in the appendix) is often quite small  (e.g. zero in skate and "courses", 8.4 in m5n10, 13 in m5n20, 30 in tshirt,...), this is because the strategy does a good job of asking the question that gives more information, and often only “sparse” information about the voting rule is enough. Similarly, the average number of questions asked to a voter is also reasonable (e.g questions per agent 6.5 in courses, 6.1 in m5n10,  )
%: X.X in Experiment YY, for instance. In Table 2, the (10,20) example shows that to reach a “low” regret -that we define as n/10- we need to ask 340 questions. This number should be divided among the voters and the chair, resulting in ~ 10 questions per voter, which we consider a reasonable amount. The fact that asking too many questions to the chair is not worth it isworth is also displayed in Table 3 in the main text.
Note that the process could be terminated early: one could decide to stop after a fixed number of questions is asked (even if regret is not zero) and to output as an “approximate winner” the alternative with lowest regret.
%If the paper will be accepted, we will stress more this point and include the Appendix Table in the final version.
\end{document}
